Wood density and the growth-dependent & independent mortality

### 2015-04-07 ms.Rmd
Option to use differnt growth measures

```{r dependencies, echo=FALSE, message=FALSE,warning=FALSE}
source('R/utils.R')
load('output/rho_stan_model.rda')
library(rstan)
```

@@

![Fig1](figures/wyckoff2002.png)

@@

![Fig2](figures/wright2010.jpg)

@@

![Fig3](figures/kraft2010.png)

@@

![Fig4](figures/chave2009.png)

@@

```{r Model output, echo=FALSE}
print(stan_model,probs = c(0.025,0.975), digits_summary = 3)
```

```{r Coefficient plot, fig.height=6,fig.width=6, echo=FALSE}
coeff_plot(stan_model, params=c('c1','c0_mu','b1','b0_mu','a1','a0_mu'),
           labels = c('ho x wd','ho','beta x wd','beta','alpha x wd','alpha'),
           xlab = 'cloglog effect size', transform = NULL)
```

@@

```{r Hazard rates,fig.height=6,fig.width=6, echo=FALSE}
par(mfrow=c(2,1),mar=c(4,3,1,1), xaxs='i')
plot_mortality(model_fit = stan_model ,model_data = stan_data, cov_name = 'rho',
               wd_values = c(200,800), growth_name = 'dbh_dt', mortality_curve = FALSE, xaxis_on = FALSE, haz_lim=c(0,2))

plot_mortality(model_fit = stan_model ,model_data = stan_data, cov_name = 'rho',
               wd_values = c(200,800), growth_name = 'dbh_dt', mortality_curve = TRUE, xaxis_on = TRUE, legend = FALSE)
```

@@

```{r 3d plots, fig.height=10,fig.width=10, echo=FALSE}
par(mfrow=c(2,1))
plot3d(model_fit = stan_model, 
        model_data = stan_data, cov_name = 'rho', 
        wd_values = seq(200,800, by=10), 
        theta=145, phi=20,mortality_curve = FALSE)

plot3d(model_fit = stan_model, 
       model_data = stan_data, cov_name = 'rho', 
       wd_values = seq(200,800, by=10), 
       theta=145, phi=20,mortality_curve = TRUE)
```

@@

StanModel <- '
  data {
    int<lower=0> n_obs;
    int<lower=0, upper=1> y[n_obs];
    int<lower=0> n_spp;
    int<lower=1> spp[n_obs];
    vector[n_obs] census_length;
    vector[n_obs] dbh_dt;
    vector[n_spp] rho;
  }
transformed data { // centers and standardizes predictors
  vector[n_spp] cs_lnrho;
  vector[n_obs] s_dbh_dt;
  cs_lnrho <- (log(rho) - mean(log(rho)))/ (2*sd(log(rho)));
  s_dbh_dt <- dbh_dt/ (2*sd(dbh_dt)); 
}
parameters { // assumes uniform priors on all parameters
  real a0_raw[n_spp];
  real b0_raw[n_spp];
  real c0_raw[n_spp];
  real a1; // effect of rho on a_log
  real b1; // effect of rho on b_log
  real c1; // effect of rho on ho_log
  real a0_mu; // a_log effect for average species
  real<lower=0> a0_sigma; // a_log effect species variation
  real b0_mu;  // b_log effect for average species
  real<lower=0> b0_sigma; // b_log effect species variation
  real c0_mu;  // ho_log effect for average species
  real<lower=0> c0_sigma; // ho_log effect species variation
}

@@

  for (i in 1:n_obs) { // Estimate p
    p[i] <- inv_cloglog(log(census_length[i] * (exp(log_a[spp[i]] - exp(log_b[spp[i]]) * s_dbh_dt[i]) + exp(log_ho[spp[i]]))));
  }
}

>>>>

@@

<!-- ![Fig1](figures/wyckoff2002.png) -->

@@

<!-- ![Fig2](figures/wright2010.jpg) -->

@@

<!-- ![Fig3](figures/kraft2010.png) -->

@@

<!-- ![Fig4](figures/chave2009.png) -->

@@

```{r Model output, echo=FALSE}
print(stan_output_combined,probs = c(0.025,0.975), digits_summary = 3)
```

```{r Coefficient plot, fig.height=6,fig.width=6, echo=FALSE}
coeff_plot(stan_output_combined, params=c('c1','c0_mu','b1','b0_mu','a1','a0_mu'),
           labels = c('ho x wd','ho','beta x wd','beta','alpha x wd','alpha'),
           xlab = 'cloglog effect size', transform = NULL)
```

@@

```{r Hazard rates,fig.height=6,fig.width=6, echo=FALSE}
par(mfrow=c(2,1),mar=c(4,3,1,1), xaxs='i')
plot_mortality(model_fit = stan_output_combined ,model_data = stan_data, cov_name = 'rho',
               wd_values = c(200,800), growth_name = 'growth_dt', mortality_curve = FALSE, xaxis_on = FALSE, haz_lim=c(0,2))

plot_mortality(model_fit = stan_output_combined ,model_data = stan_data, cov_name = 'rho',
               wd_values = c(200,800), growth_name = 'growth_dt', mortality_curve = TRUE, xaxis_on = TRUE, legend = FALSE)
```

@@

```{r 3d plots, fig.height=10,fig.width=10, echo=FALSE}
par(mfrow=c(2,1))
plot3d(model_fit = stan_output_combined,
        model_data = stan_data, cov_name = 'rho',
        wd_values = seq(200,800, by=10),
        theta=145, phi=20,mortality_curve = FALSE)

plot3d(model_fit = stan_output_combined,
       model_data = stan_data, cov_name = 'rho',
       wd_values = seq(200,800, by=10),
       theta=145, phi=20,mortality_curve = TRUE)
```

@@

StanModel <- '
  data {
    int<lower=0> n_obs;
    int<lower=0, upper=1> y[n_obs];
    int<lower=0> n_spp;
    int<lower=1> spp[n_obs];
    vector[n_obs] census_length;
    vector[n_obs] growth_dt;
    vector[n_spp] rho;
  }
transformed data { // centers and standardizes predictors
  vector[n_spp] cs_lnrho;
  vector[n_obs] s_growth_dt;
  cs_lnrho <- (log(rho) - mean(log(rho)))/ (2*sd(log(rho)));
  s_growth_dt <- growth_dt/ (2*sd(growth_dt));
}
parameters { // assumes uniform priors on all parameters
  real a0_raw[n_spp];
  real b0_raw[n_spp];
  real c0_raw[n_spp];
  real a1; // effect of rho on a_log
  real b1; // effect of rho on b_log
  real c1; // effect of rho on ho_log
  real a0_mu; // a_log effect for average species
  real<lower=0> a0_sigma; // a_log effect species variation
  real b0_mu;  // b_log effect for average species
  real<lower=0> b0_sigma; // b_log effect species variation
  real c0_mu;  // ho_log effect for average species
  real<lower=0> c0_sigma; // ho_log effect species variation
}

@@

  for (i in 1:n_obs) { // Estimate p
    p[i] <- inv_cloglog(log(census_length[i] * (exp(log_a[spp[i]] - exp(log_b[spp[i]]) * s_growth_dt[i]) + exp(log_ho[spp[i]]))));
  }
}
